Variational Monte Carlo on bosonic systems

### 2018-02-27 project_1/article/article.tex
Add subsection for the drift force

>>>>

    \subsection{The drift force}
        A disadvantage in the use of the brute-force Metropolis algorithm is
        that we might be spending much computational resources in an
        uninteresting part of configuration space. To make smarter moves we will
        use the Metropolis-Hastings algorithm (which will be discussed in due
        time). This algorithm is dependent on the drift force of the system.
        \begin{align}
            \vf{F}(\vf{r})
            &=
            \frac{2\nabla\Psi_T(\vf{r})}{\Psi_T(\vf{r})}.
        \end{align}
        Using this expression we are able to move towards parts of
        configuration space where the gradient increases or decreases yielding a
        better choice of movements.
